### 2017-03-19 paper/paper.tex
Minted

\input{config.tex}
\usepackage{hyperref}
\usepackage{float}
\usepackage{amsmath}
\usepackage{mathtools}

\newcommand\tab[1][1cm]{\hspace*{#1}}

\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black
}
\usepackage{pseudocode}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.14}

\addbibresource{sample.bib}

@@

\begin{lstlisting}
let helloWorld: string = 'Hello World' // This is a comment
console.log(helloWorld)
\end{lstlisting}

@@

\begin{lstlisting}
ballots: number[][] // Ex. [[0,1,2],[1,0,2],...]
seats: number // Ex. 2
\end{lstlisting}

@@

\begin{lstlisting}
let results: Result[] = []
// Loops over prefrences and adds/increments result
for (var i = 0; i < firstPrefrences.length; i++) {
    // Finds index in results array of candidate at i
    let index = results.findIndex(obj => obj.cand === firstPrefrences[i])
    // If candidate is not added to results
    if (index === -1) {
        results.push({ cand: firstPrefrences[i], votes: 1 })
    } else {
        // Increment count if already added in results
        results[index].votes += 1;
    }
}
\end{lstlisting}

@@

\begin{lstlisting}
// Sorts array by number of votes
results.sort((a, b) => {
    if (a.votes > b.votes) {
        return -1
    } else if (a.votes < b.votes) {
        return 1
    }
    return 0
})
// Gets the first elements in the sorted array i.e the winners
let winners = results.slice(0, seats)
// Returns array of winners
return winners.map(cand => cand.cand)
\end{lstlisting}

@@

\lstinputlisting[language=JavaScript, label=some-code, caption=Some Code]{code/candidateNode.txt}

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[table,xcdraw]{xcolor}
\usepackage{hyperref}
\usepackage{float}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{tikz}
\usepackage{pgfplots}

\pgfplotsset{compat=1.14}

\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black
}

\usepackage[backend=biber,style=authoryear]{biblatex}
\usepackage[newfloat]{minted}
\usepackage{csquotes}

\graphicspath{ {images/} }

\usemintedstyle{vs}

\newcommand\tab[1][1cm]{\hspace*{#1}}
\SetupFloatingEnvironment{listing}{name=Code example}
\definecolor{bg}{rgb}{0.95,0.95,0.95}
\newcounter{codecounter}
\newenvironment{code}{\captionsetup{type=listing}}{}

\newcommand\codeblock[3]{%
\begin{code}
	\caption{#3}
	\inputminted[%
	    mathescape,
	    linenos,
	    numbersep=5pt,
	    tabsize=4,
	    label=Helloworld,
	    bgcolor=bg,
	    breaklines%
	]{TypeScript}{#1}
	\label{#2}
\end{code}
}

\addbibresource{sample.bib}
\usepackage{caption}

@@

\codeblock{code/typescriptexample.ts}{code:typescript example}{Basic Typescript syntax}

@@

\codeblock{code/fptp/inputs.ts}{code:fptp inputs}{Inputs for FPTP program}

@@

\codeblock{code/fptp/processing.ts}{code:fptp processing}{Processing and formatting of data}

@@

\codeblock{code/fptp/result.ts}{code:fptp result calculation}{Finding and returning winning candidates}

@@

%\lstinputlisting[language=JavaScript, label=some-code, caption=Some Code]{code/candidateNode.txt}

### 2017-03-19 paper/test.tex
Minted

\documentclass{article}
\usepackage{minted}
\usepackage{xcolor}
\usemintedstyle{vs}
\definecolor{bg}{rgb}{0.95,0.95,0.95}
\begin{document}
\begin{minted}[mathescape,
               linenos,
               numbersep=5pt,
               tabsize=4,
               label=Helloworld,
               bgcolor=bg,
               breaklines]{TypeScript}
interface Result {
   cand: number,
   votes: number
}
// Calculates the winners in a First-past-the-post election
export default function calculateWinners(input: number[][], seats: number) {

   // Maps input to first prefrences
   let firstPrefrences = input.map(el => {
       return el[0]
   })

   let results: Result[] = []
   // Loops over prefrences and adds/increments result
   for (var i = 0; i < firstPrefrences.length; i++) {
       // Finds index in results array of candidate at i
       let index = results.findIndex(obj => obj.cand === firstPrefrences[i])
       // If candidate is not added to results
       if (index === -1) {
           results.push({ cand: firstPrefrences[i], votes: 1 })
       } else {
           // Increment count if already added in results
           results[index].votes += 1;
       }
   }

   // Sorts array by number of votes
   results.sort((a, b) => {
       if (a.votes > b.votes) {
           return -1
       } else if (a.votes < b.votes) {
           return 1
       }
       return 0
   })

   // Gets the first elements in the sorted array i.e the winners
   let winners = results.slice(0, seats)

   // Returns array of winners
   return winners.map(cand => cand.cand)
}

\end{minted}
\end{document}

>>>>

\documentclass{article}
\usepackage{minted}
\usepackage{xcolor}
\usemintedstyle{vs}

\renewcommand{\listingscaption}{Code example}
\newcommand{\codeblock}[3]{%
\definecolor{bg}{rgb}{0.95,0.95,0.95}

\begin{listing}[H]
  \inputminted[
    mathescape,
    linenos,
    numbersep=5pt,
    tabsize=4,
    label=Helloworld,
    bgcolor=bg,
    breaklines
  ]{TypeScript}{#1}
  \caption{#3}
  \label{#2}
\end{listing}
}

\begin{document}
\codeblock{code/candidateNode.ts}{code: global data structure}{This is an example}
\end{document}
